---
title: "Scale Calculation"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params: 
  authors: "Authors are anonymized"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

#### `r params$authors` {-}


```{r setup, include=FALSE}
options(digits=3)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gtsummary)
dat <- read_rds(here::here("data", "final_data.rds"))
```



# Calculating scales

In the following section we calculate the scales used in our survey. 

## Big Five

An exploratory factor analysis using MinRes shows, that the OCEN scales work well.
However, the A scale seems to be confounded with answering tendency (skewd towards answering with agree).
This is however, also explainable since agreebleness would measure how much people answer "agree" on a survey.


```{r bigfive}
dat %>% select(starts_with("b5")) %>% 
  psych::fa(nfactors = 5)
```


```{r bigfive_individual}
dat %>% select(starts_with("b5_o")) %>% 
  psych::alpha(check.keys = T) -> bfoa

dat %>% select(starts_with("b5_c")) %>% 
  psych::alpha(check.keys = T) -> bfca

dat %>% select(starts_with("b5_e")) %>% 
  psych::alpha(check.keys = T) -> bfea

dat %>% select(starts_with("b5_a")) %>% 
  psych::alpha(check.keys = T) -> bfaa

dat %>% select(starts_with("b5_n")) %>% 
  psych::alpha(check.keys = T) -> bfna

```

## Scale Reliability Big Five

The reliability of our scales vary from:

- openness Cronbach's $\alpha = `r bfoa$total$std.alpha`$,
- conscientiousness   $\alpha = `r bfca$total$std.alpha`$,
- extraversion   $\alpha = `r bfea$total$std.alpha`$,
- agreeableness   $\alpha = `r bfaa$total$std.alpha`$,
- and neuroticism   $\alpha = `r bfna$total$std.alpha`$.


