---
title: "Hypothesis Tests H2"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params: 
  authors: "Authors are anonymized"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
---

#### `r params$authors` {-}


```{r setup, include=FALSE}
options(digits=3)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gtsummary)
library(apastats)
library(hrbrthemes)
dataset <- read_rds(here::here("data", "final_data.rds"))

ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())

```



# Hypothesis 2: Personality Traits  

The Big Five personality traits influence the awareness of filter bubbles regarding political opinion formation (differently in different countries).  

Analyzed Variables:  

* agreeableness  
* conscientiousness  
* extraversion  
* neurotism  
* openness to experience 


## Agreeableness 

The data is not distributed normally for both the nationality and awareness groups.  

For nationality, the Barlett test was significant ($\chi^2=12.40$, $df = 4$, $p < .05$) thus not satisfying the ANOVA condition of homogeneity of variances. Under these conditions, the level of agreeableness was significantly different depending on nationality ($F(4, 1233) = 9.35$, $p < .05$).  The Tukey post-hoc test showed that there was a significant difference between:  

* Poland \& Netherlands
* Poland \& Germany 
* Poland \& France 

For awareness, the Barlett test was nog significant ($\chi^2=2.42$, $df = 2$, $p > .05$) thus satisfying the ANOVA condition of homogeneity of variances. The level of agreeableness did not significantly differ between the awareness groups ($F(2, 1235)=0.80$, $p>.05$). However, there was an interaction effect of nationality and awareness on the level of agreeableness ($F(8, 1223) = 2.05$, $p < .05$). However, the post hoc test showed that there were only a few instances for which the interaction effect was significant. 








```{r}
ggplot(dataset) + 
  aes(y = left_right) +
  aes(x = nationality) +
  geom_jitter(alpha = 0.5) + 
  facet_wrap(vars(awareness))


model <- lm(left_right ~ nationality + awareness, data = dataset)
amodel <- anova(model) 

model %>% apastats::describe.Anova()
plot(model)




dataset %>% ggplot() +
  aes(x = left_right, y = awareness, color = nationality, group = nationality) +
  stat_summary() +
  geom_line(stat = "summary")




dataset %>% ggplot() +
  aes(x = left_right, y = awareness, color = nationality, group = nationality) +
  geom_jitter() +
  #geom_smooth(method = "lm")
  #stat_summary() +
  # geom_line(stat = "summary") +
  facet_wrap(vars(nationality))
  NULL
```


```{r}
library(seminr)
  

dataset %>% select(left_right, awareness, education, starts_with("b5")) %>% na.omit() -> sem_data  

to_num <- function(x) {
  as.numeric(as.factor(x))
}

h_to_num <- function(x) {
  as.numeric(haven::as_factor(x))
}

sem_data <- sem_data %>% 
  mutate_if(is.character, to_num) %>% 
  mutate_if(is.factor, to_num) %>% 
  mutate_if(haven::is.labelled, h_to_num)


measurement_model <- seminr::constructs(
  seminr::composite("left right", single_item("left_right")),
  composite("filterbubble awareness", single_item("awareness")),
  composite("demo education", single_item("education")),
  composite("agreeableness", single_item(c("b5_a1", "b5_a2")))
)

structural_model <- seminr::relationships(
  paths(from = "agreeableness", to = "left right"),
  paths(from = "filterbubble awareness", to = "left right"),
  paths(from = "demo education", to = c("filterbubble awareness", "left right"))
)


pls_model <- estimate_pls(measurement_model = measurement_model, 
                          structural_model = structural_model, 
                          data = sem_data)

boot_model <- bootstrap_model(pls_model)

plot(boot_model)
  
```

